\documentclass[12pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage[top=2cm, bottom=2cm, left=1.5cm, right=1.5cm]{geometry}
\usepackage{times}
\usepackage{titlesec}
\usepackage{fancyhdr}

\titleformat{\section}
  {\normalfont\small}{\Roman{section}.}{1em}{}

\renewcommand{\thesection}{\Roman{section}}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{SMA Ignatius Global School (IGS) Palembang}
\fancyhead[R]{Cryptocurrency Investment}
\fancyfoot[C]{\thepage}

\title{\Huge\textbf{A twenty-four-hour Cryptocurrency Investment Strategy for Bitcoin, Ethereum and XRP}}
\author{Zebe Khemako - 22.1684 dan Bryan Marcello Subandi - 22.1292 \\
        Ilmu Pengetahuan Alam (Komputer) \\
        SMA Ignatius Global School (IGS) Palembang \\
        Jl. Mayor Ruslan No. 118 Palembang \\
        \texttt{email@students.ignatiusglobal.sch.id}}
\date{}

\begin{document}

\maketitle

\begin{abstract}
    This Economic Research Paper focuses on the analysis of short-term investments in cryptocurrencies-by-the-hour. The focus of the study will be on Bitcoin (BTC), Ethereum (ETH), and XRP. The study will present facts on current market trends, historical volatilities, and analysts' input on whether these could form short-term investment assets. 
\end{abstract}

\section{Introduction}
This study looks into short-term investment in cryptocurrency as a market that is characterized by extreme volatility and instantaneous price change; it presents opportunities and threats. The purpose of the study shall be to evaluate the feasibility of this model for investment in cryptocurrency over the short term of a day. Considering only three critical coins will mean evaluating the potential profit or loss prospect based on current values in Bitcoin, Ethereum, and XRP.

\section{Methodology}

Quantitative and qualitative methods will be used in this research.
\begin{itemize}
    \item Market Data Analysis: Examine historical price data on BTC, ETH, and XRP in 24-hour intervals so that patterns and trend analyses can be drawn, as well as possible models for predicting prices. Make use of technical indicators, such as Moving Averages, the Relative Strength Index, and Bollinger Bands-to track potential short-term price activity.

    \item Expert opinion analysis: Gather and review financial periods, analyst reports, and social media sentiment regarding the short-term price movements in selected cryptocurrencies.
\end{itemize}

\section{Analysis}
\begin{itemize}
    \item Bitcoin (BTC): 
    \begin{itemize}
        \item Strengths: Dominance in the cryptocurrency market, strong brand recognition and history, and potentially high price value in the long run.
        \item Weaknesses: High risk short-term trading due to high volatility, regulatory barriers, and government intervention targeted towards Bitcoin.
    \end{itemize}

    \item Ethereum (ETH): 
    \begin{itemize}
        \item Strengths: increase for both decentralized finance and non-fungible tokens, potential for further development and increased usage

        \item Weaknesses: high competition from other blockchain platforms, Network congestion, and scaling issues are evidence of vulnerability.
    \end{itemize}

    \item XRP (XRP):
    \begin{itemize}
        \item Strengths: low transaction fees with very fast transaction speeds, potential for development in cross-border payment and remittance applications.

        \item Weaknesses: Ongoing legal challenges, coupled with regulatory uncertainty and little utility when compared to other forms of crypto currency.
    \end{itemize}

\end{itemize}

 \section{Findings and Discussion}
This section will assess profit/loss potential for each cryptocurrency within 24 hours, identify key short-term risks, analyze the impact of market volatility and investor sentiment on investment outcomes, and formulate trading strategies to maximize returns and minimize risks within the 24-hour time frame.

The market value of BTC, ETH, and XRP during the last 24 hours is as such:
\begin{itemize}
    \item Bitcoin (BTC)
    \begin{itemize}
        \item Current Price: \verb|$96,413.00|
        \item 24-Hour Change: \verb|0.86%|
        \item Market Cap: \verb|$1,910,101,981,356|
    \end{itemize}

    \item Ethereum (ETH)
    \begin{itemize}
        \item Current Price: \verb|$3,435.85|
        \item 24-Hour Change: \verb|0.64%|
        \item Market Cap: \verb|$414,014,477,635|
    \end{itemize}

    \item XRP (XRP)
    \begin{itemize}
        \item Current Price: \verb|$2.42|
        \item 24-Hour Change: \verb|1.86%|
        \item Market Cap: \verb|$138,780,002,176|
    \end{itemize} 
    
\end{itemize}

With the following information we can conclude that Bitcoin indicates a modest potential for short-term profits while XRP shows the highest potential for short-term profits with Ethereum having the lowest potential of the three cryptocurrencies

\section{Conclusion}
Short-term cryptocurrency investment within 24 hours brings great opportunities, as well as risks that are quite crucial. This showcases the importance of keenly analyzing the market, assessing risk, and setting a defined plan for investing. While Bitcoin, Ethereum, and XRP offer varying degrees of potential, investors must exercise caution due to the inherent volatility of the cryptocurrency market..



   
   
   

  



\end{document}
